### 2020-05-01 final_report/appendix_online.tex
run spellcheck

In this appendix, we provide a brief overview of datasets, software, documentation 
and other resources available online for public use. All files related to this
project are hosted by GitHub in a group at
\url{https://github.com/ucl-tbr-group-project}, organised as follows:
\begin{description}
	\item[\href{https://github.com/ucl-tbr-group-project/simple-sphere-study}{Simple Sphere Study}]
		OpenMC TBR simulation software used to generate TBR values.
	\item[\href{https://github.com/ucl-tbr-group-project/sampling}{Sampling}]
		Python implementation of the Approximate TBR Evaluator.
	\item[\href{https://github.com/ucl-tbr-group-project/data}{Data}]
		Over \num{900000}~datapoints and TBR values generated in sampling runs 0-2.
	\item[\href{https://github.com/ucl-tbr-group-project/regression}{Regression}]
		Python implementation of the surrogate models presented in this work as
		well as various pre-processing, plotting and evaluation tools.
	\item[\href{https://github.com/ucl-tbr-group-project/hyperopt}{Hyperparameter Optimisation}]
		Results, plots and software commands used to produce them.
	\item[\href{https://github.com/ucl-tbr-group-project/documentation}{Documentation}]
		Notes, extended bibliography, this \LaTeX\  document and source files.
\end{description}

>>>>

In this appendix, we provide a brief overview of datasets, software, documentation 
and other resources available online for public use. All files related to this
project are hosted by GitHub in a group at
\url{https://github.com/ucl-tbr-group-project}, organised as follows:
\begin{description}
	\item[\href{https://github.com/ucl-tbr-group-project/simple-sphere-study}{Simple Sphere Study}]
		OpenMC TBR simulation software used to generate TBR values.
	\item[\href{https://github.com/ucl-tbr-group-project/sampling}{Sampling}]
		Python implementation of the Approximate TBR Evaluator.
	\item[\href{https://github.com/ucl-tbr-group-project/data}{Data}]
		Over \num{900000}~datapoints and TBR values generated in sampling runs 0-2.
	\item[\href{https://github.com/ucl-tbr-group-project/regression}{Regression}]
		Python implementation of the surrogate models presented in this work as
		well as various preprocessing, plotting and evaluation tools.
	\item[\href{https://github.com/ucl-tbr-group-project/hyperopt}{Hyperparameter Optimisation}]
		Results, plots and software commands used to produce them.
	\item[\href{https://github.com/ucl-tbr-group-project/documentation}{Documentation}]
		Notes, extended bibliography, this \LaTeX\  document and source files.
\end{description}

### 2020-05-01 final_report/data.tex
run spellcheck

With a grid search in such a high-dimensional domain clearly intractable, we
selected uniform pseudo-random sampling\footnote{Continuous and discrete
parameters are drawn from a corresponding uniform distribution over their
domain, as defined in~\cref{tbl:params}. For reproducibility, each run uses a seed equal to its number.} to generate large amounts of feature
configurations that we consider to be independent and unbiased. For evaluation
of the expensive MC TBR model, we utilise parallelisation offered by
the HPC infrastructure available at UCL computing facilities. To this end, we
designed and implemented the Approximate TBR Evaluator---a Python software package capable of
sequential evaluation of the multi-threaded OpenMC simulation on batches of
previously generated points in the feature space.
Having deployed ATE at the UCL Hypatia cluster\footnote{The Hypatia RCIF
	partition is comprised of 4~homogeneous nodes. Each node is installed with
	376~GB RAM and 40~Intel\textsuperscript{\textregistered}
	Xeon\textsuperscript{\textregistered} Gold 6148 CPUs of clock frequency
	2.40~GHz.}, we completed three data
generation runs that are summarised in~\cref{tbl:sampling-runs}.

>>>>

With a grid search in such a high-dimensional domain clearly intractable, we
selected uniform pseudo-random sampling\footnote{Continuous and discrete
parameters are drawn from a corresponding uniform distribution over their
domain, as defined in~\cref{tbl:params}. For repeatability, each run uses a seed equal to its number.} to generate large amounts of feature
configurations that we consider to be independent and unbiased. For evaluation
of the expensive MC TBR model, we utilise parallelisation offered by
the HPC infrastructure available at UCL computing facilities. To this end, we
designed and implemented the Approximate TBR Evaluator---a Python software package capable of
sequential evaluation of the multi-threaded OpenMC simulation on batches of
previously generated points in the feature space.
Having deployed ATE at the UCL Hypatia cluster\footnote{The Hypatia RCIF
	partition is comprised of 4~homogeneous nodes. Each node is installed with
	376~GB RAM and 40~Intel\textsuperscript{\textregistered}
	Xeon\textsuperscript{\textregistered} Gold 6148 CPUs of clock frequency
	2.40~GHz.}, we completed three data
generation runs that are summarised in~\cref{tbl:sampling-runs}.

### 2020-05-01 final_report/methodology.tex
run spellcheck

\Cref{tbl:metrics} provides an exhaustive listing and description of metrics recorded
in our experiments. For regression performance analysis, we include a selection
of absolute metrics to assess the approximation capability of surrogates, and set
practical bounds on the expected uncertainty of their predictions. In addition, we also track
relative measures that are better-suited for comparison between this work and others, as
they maintain invariance with respect to the selected domain and image space.
For complexity analysis, surrogates are assessed in terms of wall
time\footnote{Real time elapsed during computation measured by a
chronometer, here by means of the Python~\texttt{time} package.}
elapsed during training and predicition. This is motivated by common practical use
cases of our work, where models are trained and used as drop-in replacements for the
expensive MC TBR model. Since training set sizes remain to be determined, all times are
reported per a single datapoint. Even though some surrogates support acceleration
by means of parallelisation, sequential processing of samples was ensured to
achieve comparability between considered
models.\footnote{The only exception to this are artificial neural networks,
	which require considerable amount of processing power for training on conventional CPU architectures.}

>>>>

\Cref{tbl:metrics} provides an exhaustive listing and description of metrics recorded
in our experiments. For regression performance analysis, we include a selection
of absolute metrics to assess the approximation capability of surrogates, and set
practical bounds on the expected uncertainty of their predictions. In addition, we also track
relative measures that are better-suited for comparison between this work and others, as
they maintain invariance with respect to the selected domain and image space.
For complexity analysis, surrogates are assessed in terms of wall
time\footnote{Real time elapsed during computation measured by a
chronometer, here by means of the Python~\texttt{time} package.}
elapsed during training and prediction. This is motivated by common practical use
cases of our work, where models are trained and used as drop-in replacements for the
expensive MC TBR model. Since training set sizes remain to be determined, all times are
reported per a single datapoint. Even though some surrogates support acceleration
by means of parallelisation, sequential processing of samples was ensured to
achieve comparability between considered
models.\footnote{The only exception to this are artificial neural networks,
	which require considerable amount of processing power for training on conventional CPU architectures.}
